Spatial Analysis of Russian Law Firm Names

### 2024-07-29 law-firms-names/Paper.Rmd
Edit methods: law firms definition, period of analysis, SMB data preprocessing, firm names embeddings, #5

The downloadable version of the registry includes, in particular, firm names, addresses of registration (up to a settlement), and codes of activity kinds according to the National Classification of Economic Activities (NCAE). It should be noted that the registry does not include large firms, resulting in some data being absent. Nevertheless, the majority of commercial law firms in Russia (in excess of 75%) are classified as small and medium-sized businesses and thus are included in the registry. Consequently, the availability of information is relatively high, and it can be used to draw reliable conclusions.

@@

### 2.2.1. FTS data processing

SMB registry dumps from FTS website have a large volume (≈200 Gb in total) and a complex structure: each dump is an archive of several thousand XML files, and each XML file contain 900 records with various information about organisations and individuals. Dumps are monthly, resulting in ≈90 archives for the period from 2016 to the present. If unpacked, all archives would occupy more than 2 Tb of disk space, and the extraction and preprocessing of such volume of data would take a large time. It should be noted, though, that the majority of information is redundant for the task in hand, because it is duplicated due to data publication specific (each archive contains a full copy of the registry, and if nothing has changed during the month, the data records will be merely the same) and because only the data about law firms is required, while the registry holds information about all the other firms as well. To extract necessary data from the raw archives, an open-source Python command-line tool was developed named ru-smb-companies. The main stages of data extractions are outlined in the next paragraph, while for the complete information about data processing workflow readers may refer to the source code of the program.

FTS data processing took several steps. First, all source archives available at the time of research (November 2023) were downloaded  from FTS servers and stored both locally and in the cloud. Next, information about law firms was extracted from each archive to a CSV file. Extracted attributes include company or person name, address of incorporation (region, district, city, settlement), taxpayer ID, main activity code and some other properties. After this, CSV tables were combined into one table, deduplicated, and raw addresses were normalized and geocoded to fix the inconsistency in location names and add geographical coordinates. Finally, the resulting table was transformed in a panel view so that each row represents one business entity at a given year. The output table contains data about ≈ 30, 000 law firms for 2016–23.

### 2.2.2. Firm names processing

A major challenge regarding the methods of this study is the working with names. The objectives of the research imply that names should be grouped and compared in some way. This can easily be accomplished with numbers, but firm names are just short text sequences. Of course, a human can easily say whether two names are similar or not and classify them. However, the human-based approach does not scale well, and the quantity of names requires automation. There are several traditional techniques allowing us to compare text strings. For example, edit distance calculates the number of atomic changed required to turn one string to another, and the edit distance between “cat” and “car” is 1, while the edit distance between “car” and “karst” is 3. Another method named n-gram similarity splits the strings into subsequences, or tokens, and finds the number of common tokens, so that “law company” and “law bureau” are more close to each other than “law bureau” and “juridical center”. Despite their simplicity, they also have a significant disadvantage: they cannot account for the intrinsic variability and flexibility of language and do not consider the meaning of the words and phrases rather than their formal representation. For instance, a human understands that “law company” and “legal organisation” mean almost the same, while edit distance between these strings is high, and n-gram similarity is low. A modern method called text embeddings (sometimes referred to as vectors) can deal with this issue and therefore it is used for this research.

Text embedding, or vector, is a numeric representation of a word, sentence or a document usually designed to catch the meaning of the text. An embedding typically looks like just a sequence of decimals with fixed length, i.e. the count of elements in this sequence does not depend on the length of the input text, so that a short sentence or an entire paragraph are represented as a sequence of, say, 256 numbers. Vectors allow simple computations to find out whether they are more or less similar to each other, and the similarity of vectors corresponds to the similarity of texts. Thus, by computing a mathematical distance between embeddings, one can conclude about the semantic distance between texts. This is right the case of firm names comparison, similarity, and grouping.

There are various methods of obtaining embeddings for different texts, e.g. Word2Vec, GloVe, FastText. The newest GPT-based pretrained large language models such as ChatGPT are also capable of producing text vectors. For this study, embeddings from YandexGPT model were used. These embeddings were obtained for each unique firm name via public API of the model. The vector dimensionality is 256, i.e. each vector is a sequence of 256 numbers. All the concrete hypothesis testing techniques outlined in the next subsection are based on the use of these vectors.

@@

### 2.2.4. Other important considerations

The time range of the source data is from 2016 to 2023. Only the firms that have existed for at least 3 years are included in the analysis. Only organizations are studied, while individual entrepreneurs are omitted, because they do not have firm names. Firm names are preprocessed to remove any parts pointing to the legal form of the business (e.g. limited liability company or public stock company), because these parts are common to the majority of names and thus do not add anything valuable. Law firms are selected by filtering using the following condition: main activity code equals 69.10 (activity in the area of law according to All-Russia Classifier of Kinds of Economic Activity). This filtering technique is derived from @Moiseeva2016.

>>>>

The downloadable version of the registry includes, in particular, firm names, addresses of registration (up to a settlement), and codes of activity kinds according to the National Classification of Economic Activities (NCEA). It should be noted that the registry does not include large firms, resulting in some data being absent. Nevertheless, the majority of commercial law firms in Russia (in excess of 75%) are classified as small and medium-sized businesses and thus are included in the registry. Consequently, the availability of information is relatively high, and it can be used to draw reliable conclusions.

@@

### 2.2.1. Law firms selection criteria

In this study, the term “law firm” is defined as a commercial organisation registered in Russia in accordance with the Civil Code of Russia, with a main activity code equal to 69.10 (activity in the area of law) according to NCEA. The aforementioned definition excludes individual entrepreneurs, foreign companies, non-profit organisations, advocacy firms, and notaries. The selection technique based on the main activity code was derived from that proposed by @Moiseeva2016. Individual entrepreneurs were excluded from the analysis, because they typically operate under their personal names, and even if they have a brand, it is not listed in the SMB registry. Other types of firms were not included in the analysis primarily due to data availability issues.

The analysis covers a period of six years, from 2016 to 2021. The initial point in time is defined by the commencement of SMB registry data availability. Although data for 2022 and subsequent years are available, they have not been studied as the ongoing war may have had a significant impact on both the economy and the dissemination of information by government bodies. The purpose of this research is to provide conclusions about the space and names under “normal” conditions, and it would therefore be unwise to consider data collected during the period when the circumstances are away from normal. Organisations with a lifespan of less than three years have been omitted from the research, which are likely to be dummy companies.

### 2.2.2. Firm data acquisition

The processing of SMB registry data was conducted in a series of stages. In the initial phase of the research process, all source archives were downloaded. Each source archive contained a full copy of the registry data for the specified publication date, with a new archive becoming available on a monthly basis. Subsequently, data pertaining to law firms was extracted from the archives and stored in CSV files. Each CSV file contained data from one source archive. Subsequently, all CSV files were consolidated into a single table, the duplicated records were removed, and the remaining records were augmented with start and end temporal markers. Subsequently, the addresses were normalised to resolve the inconsistencies in location names and geocoded to add geographical coordinates. Finally, the resulting table was transformed into a panel view, with each row representing a single law firm at a given year. All these stages were implemented in an open-source Python command-line tool.

### 2.2.3. Firm names embeddings retrieval

The Yandex Foundation Models cloud service was used to transform the firm names into text vectors, or embeddings. The “text-search-query” model was selected because its purpose, as stated in the documentation, is to vectorise short texts. Prior to vectorisation, the firm names were preprocessed to remove indications of organisational form such as “limited liability company”. This was done because such indications are common to the majority of names and thus have little value. The results of the queries to the models API were stored separately for reuse, given that API calls are paid and take a time to be completed.

@@
